\documentclass[12pt,-letter paper]{article}
\usepackage{siunitx}
\usepackage{setspace}
\usepackage{gensymb}
\usepackage{xcolor}
\usepackage{caption}
%\usepackage{subcaption}
\doublespacing
\singlespacing
\usepackage[none]{hyphenat}
\usepackage{amssymb}
\usepackage{relsize}
\usepackage[cmex10]{amsmath}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{commath}
\usepackage{amsthm}
\interdisplaylinepenalty=2500
%\savesymbol{iint}
\usepackage{txfonts}
%\restoresymbol{TXF}{iint}
\usepackage{wasysym}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{txfonts}
\let\vec\mathbf{}
\usepackage{stfloats}
\usepackage{float}
\usepackage{cite}
\usepackage{cases}
\usepackage{subfig}
%\usepackage{xtab}
\usepackage{longtable}
\usepackage{multirow}
%\usepackage{algorithm}
\usepackage{amssymb}
%\usepackage{algpseudocode}
\usepackage{enumitem}
\usepackage{mathtools}
%\usepackage{eenrc}
%\usepackage[framemethod=tikz]{mdframed}
\usepackage{listings}
%\usepackage{listings}
\usepackage[latin1]{inputenc}
%%\usepackage{color}{   
%%\usepackage{lscape}
\usepackage{textcomp}
\usepackage{titling}
\usepackage{hyperref}
%\usepackage{fulbigskip}   
\usepackage{tikz}
\usepackage{graphicx}
\lstset{
  frame=single,
  breaklines=true
}
\let\vec\mathbf{}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{siunitx}
\let\vec\mathbf{}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{tfrupee}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mwe} % for blindtext and example-image-a in example
\usepackage{wrapfig}
\providecommand{\mydet}[1]{\ensuremath{\begin{vmatrix}#1\end{\vmatrix}}}
\providecommand{\myvec}[1]{\ensuremath{\begin{bmatrix}#1\end{b\matrix}}}
\providecommand{\cbrak}[1]{\ensuremath{\left\{#1\right\}}}
\providecommand{\brak}[1]{\ensuremath{\left(#1\right)}}
\providecommand{\sbrak}[1]{\ensuremath{{}\left[#1\right]}}
\title{\textbf{Math Olympiad}}
\date{}
\begin{document}
\maketitle{}
\begin{center}
\section*{Algebra}
\end{center}
\begin{enumerate}
\item For how many pairs of positive integers \brak{x, y} is x + 3y = 1007
\item Rama was asked by her teacher to subtract 3 from a certain number and then divide the result by 9. Instead, she subtracted 9 and then divided the result by 3. She got 43 as the answer. What would have been her answer if she had solved the problem correctly?
\item The letters $R$, $M$, and $O$ represent whole numbers. If $R \times M \times O = 240$, $R \times O + M = 46$, and $R + M \times O = 64$, what is the value of $R + M + O$?
\item Let $P$\brak{n} = \brak{n + 1}\brak{n + 3}\brak{n + 5}\brak{n + 7}\brak{n + 9} What is the largest integer that is a divisor of $P$(n) for all positive even integers n?
\item How many integer pairs \brak{x, y} satisfy $ x ^ 2 + 4y ^ 2 - 2xy - 2x - 4y - 8 =0 $?
\item Let $S_n = n^2 + 20n + 12$, $n$ a positive integer. What is the sum of all possible values of $n$ for which $S_n$ is a perfect square?
\item Suppose that $4^{x_1} = 5$, $5^{x_2} = 6$, $6^{x_3} = 7, \ldots, 126^{x_{123}} = 127$, $127^{x_{124}} = 128$. What is the value of the product $x_1 x_2 \ldots x_{124}$?
\item If
	$\frac{1}{\sqrt{2011} + \sqrt{2012}} = \frac{\sqrt{m} - \sqrt{n}}{\sqrt{m+n}},$
where $m$ and $n$ are positive integers, what is the value of $m + n$?
\item If $a = b - c$, $b = c - d$, $c = d - a$, and $abcd \neq 0$, then what is the value of $\frac{a}{b} + \frac{b}{c} + \frac{c}{d} + \frac{d}{a}$? 
\item How many non-negative integral values of $x$ satisfy the equation
    \[
    \sbrak{\frac{x}{5}} = \sbrak{\frac{x}{7}}?
    \]
    (Here $\sbrak{x}$ denotes the greatest integer less than or equal to $x$. For example, $\sbrak{3.4} = 3$ and $\sbrak{-2.3} = -3$.)
\item Let $x_1, x_2, x_3$ be the roots of the equation $x^3 + 3x + 5 = 0$. What is the value of the expression\[ \brak{ x_1 + \frac{1}{x_1} } \brak{ x_2 + \frac{1}{x_2} }\brak{ x_3 + \frac{1}{x_3}}? \]
\item What is the sum of the squares of the roots of the equation
    \[
	x^2 - 7\sbrak {x} + 5 = 0?
    \]
(Here $\sbrak{x}$ denotes the greatest integer less than or equal to $x$. For example, $\sbrak {3.4} = 3$ and $\sbrak{ -2.3} = -3$.
\end{enumerate}
\begin{center}
\section*{Probability}
\end{center}
\begin{enumerate}
\item A postman has to deliver ive letters to five different houses. Mischievously, he posts one letter through each door without looking to see if it is the correct address. In how rnany different way could he do this so that exactly two of the five houses receive the correct letters?
\end{enumerate}
\begin{center}
\section*{Geometry}
\end{center}
\begin{enumerate}
\item $PS$ is a line segment of length 4 and $O$ is the midpoint of $PS$. A semicircular arc is drawn with $PS$ as diameter. Let $X$ be the midpoint of this arc. $Q$ and $R$ are points on the arc $PXS$ such that $QR$ is parallel to $PS$ and the semicircular arc drawn with $QR$ as diameter is tangent to $PS$. What is the area of the region $QXROQ$ bounded by the two semicircular arcs?
\item $O$ and $I$ are the circumcentre and incentre of $\triangle ABC$ respectively. Suppose $O$ lies in the interior of $\triangle ABC$ and $I$ lies on the circle passing through $B$, $O$, and $C$. What is the magnitude of $\angle BAC$ in degrees?
\item In $\triangle ABC$, we have $AC = BC = 7$ and $AB = 2$. Suppose that $D$ is a point on line $AB$ such that $B$ lies between $A$ and $D$ and $CD = 8$. What is the length of the segment $BD$?
\item In rectangle $ABCD$, $AB = 5$ and $BC = 3$. Points $F$ and $G$ are on line segment $CD$ so that $DF = 1$ and $GC = 2$. Lines $AF$ and $BG$ intersect at $E$. What is the area of $\triangle ABE$?
\item A triangle with perimeter 7 has integer side lengths. What is the maximum possible area of such a triangle?
\item $ABCD$ is a square and $AB$ = 1 Equilateral triangles $AYB$ and $CXD$ are drawn such that $X$ and $Y$ are inside the square.What is the length of $XY$?
\end{enumerate}
\begin{center}
\section*{Functions}
\end{center}
\begin{enumerate}
\item Let $N$ be the set of natural numbers. Suppose $f : N \rightarrow N$ is a function satisfying the following conditions:
    \begin{enumerate}
	    \item $f\brak{mn} = f\brak{m} f\brak{n}$,
	    \item $f\brak{m} < f\brak{n}$ if $m < n$,
	    \item $f\brak{2} = 2$.
    \end{enumerate}
	What is the value of $\sum_{k=1}^{20} f\brak{k}$ ?
\end{enumerate}
\end{document}

